Psyc 601 Multivariate Statistics Project

### 2013-08-14 writeups/proposal/proposal.tex
foo
Former-commit-id: c1f2c4c918e39331eb1670719d8bc1b8b2cb6571 [formerly 321d3ae21488d07e4082b61b8c07d2c44c5a7a2a]
Former-commit-id: 8060f7fb3030f596a2624cc9f8d2a28cbeeefd10
foo
Former-commit-id: a0c904c4c347a5d5e37003cb7c16c09bdaea6888 [formerly 8db452a7d709f06293c8edfee936ac76f3b43f64]
Former-commit-id: 797f913fe18152452138192bdffb0819c2086a32

@@

\subsubsection{Comparison Between ACT-R and Vector-based Memory Systems}

@@

\subsubsection{Modeling Lifetime of a User's Hashtag}

@@

\subsubsection{Single-user-focused Hashtag Modeling}

@@

\section{Prior Work on Hashtag Prediction}

\subsection{StackOverflow}

@@

\subsection{Twitter}

FIXME: Find cite for twitter hashtag prediction

@@

@@

\subsection{Pointwise Mutual Information}

@@

\section{Matrix-based Models of Semantics}

\subsection{Latent Semantic Analysis}

@@

\subsubsection{Word Order}

\subsubsection{Comparison to PMI}

TODO: Performance and issue of scale. \cite{Budiu2007}

\section{Vector-based Models of Semantics}

@@

\subsubsection{Connection to LSA}

FIXME: Get citation.

@@

@@

@@

@@

\subsubsection{Lifetime of a User's Hashtag}

>>>>

% If the toc is too detailed, try limiting the depth of printed sections in the TOC:
% \setcounter{tocdepth}{2}

@@

\subsubsection{Comparison Between ACT-R and Vector-Based Memory Systems}

@@

\subsubsection{Single-User-Focused Hashtag Modeling}

@@

TODO: How is recency information about the hashtag included in the model?

@@

\section{Prior Research}

\subsection{Hashtag Prediction}

\subsubsection{StackOverflow}

@@

\subsubsection{Google+}

TODO: Summarize Google+ hashtag prediction \cite{GoogleKeynote2013}

\subsubsection{Twitter}

\cite{Efron2010} Generated related hashtags from 'query'.
Showed that users found those hashtags useful for the query.
Not using the model to predict hashtags from tweets, but a model like this could be used for that purpose.
They were focused more on making the case that hashtags provide useful information that can be used on sites like Twitter as part of a general recommendation system.

@@

\subsubsection{The Netflix Prize}

TODO: Summarize and \cite{Bennett2007}

\subsubsection{Recommending Twitter Users to Follow}

TODO: Summarize and \cite{Hannon2010}

@@

\subsection{Connection to Pointwise Mutual Information}

@@

\section{Latent Semantic Analysis Memory Theory}

@@

\subsection{Singular Value Decomposition}

\subsection{Word Order}

\subsection{Scaling Issues}

TODO: Compare with PMI, performance and issue of scale. \cite{Budiu2007}

\section{Vector-Based Memory Systems}

@@

\subsection{Connection to LSA}

TODO: Summarize \cite{Kanerva2000}

@@

\section{Incorporating Hashtag Recency}

\subsection{ACT-R}

TODO: ACT-R has a strong theory here.
TODO: IR literature for Twitter domain uses a model similar to ACT-R \cite{Efron2011}

\subsection{Vector-based Models}

TODO: Unclear how recency will fit in with random permutation vector-based model.

@@

TODO: common-hashtags dataset
TODO: popular-users dataset

@@

\subsubsection{StackOverflow Dataset Modifications}

TODO: Use newest dataset
TODO: Chunk tags

\subsubsection{Analyze Recency for User-Generated Hashtags}

TODO: Use stackoverflow and twitter dataset

\subsubsection{Incorporating Recency Into Random Permutations}

TODO: Use stackoverflow dataset only for random permutations

\subsubsection{Incorporating Word Order Into ACT-R}

TODO: Use twitter dataset only for ACT-R

@@

TODO: vector-based and act-r head to head on twitter
TODO: head to head on stackoverflow
